### 2023-09-01 ms.qmd
Ignore output style for now

---
date: 2023-07-18
bibliography: bibliography.bib
format:
  docx:
    reference-doc: reference.docx
  pdf:
    keep-tex: false
    documentclass: scrartcl
    classoption: twocolumn
    fontfamily: libertinus
    fontsize: 10pt
    papersize: a4
    fig-align: center
    fig-width: 8
    section-number: true
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - bottom=30mm
    include-in-header:
      - text: |
          \setlength{\columnsep}{7.5mm}
          \addtokomafont{disposition}{\normalfont}
---

>>>>

---
date: 2023-07-18
bibliography: bibliography.bib
format:
  html: default
---
